---
title: "Barcode Scanner Concatenation"
author: "Laila Sathe"
date: "9/8/2020"
output: rmarkdown::github_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file will guide you through the concatenation of multiple barcode scanner files into a single file that is compatible with Benchling.

To learn more, reference the related SOP, which can be found [HERE](https://uclahs.app.box.com/folder/121755341296).

## Input desired files
Type run name in the text input field. Then, use `ctrl` + `click` to select all desired files.

Next, click to select the desire folder to save to. Click `Submit`.

A preview will show your concatenated file. Your concatenated file will be saved with the run name in the desired folder.

```{r, echo=FALSE}
library(shiny)
library(plyr)
library(shinyFiles)


  ui <- fluidPage(
      
      sidebarLayout(
          sidebarPanel(
              textInput("text", "Run Name"),
              fileInput("file1", "Choose CSV Files", accept = ".csv", multiple=TRUE),
              shinyDirButton('folder', 'Save to', 'Please select a folder', FALSE),
              actionButton("go", "Submit"),
          ),
          
          mainPanel(
             
              tableOutput("contents"),
              #textOutput("name")
          )
      )
  )
  
  server <- function(input, output) {
    observed=reactiveValues(
            input=NULL
    )
    observe({
      volumes=getVolumes()
      roots=c(wd = 'C:')
      shinyDirChoose(input, 'folder', roots = roots, filetypes=c('', 'txt'))
      observed$input=c(isolate(observed$input),(parseDirPath(roots, input$folder)))
     
    })
 
    observeEvent(input$go, {
    output$contents <- renderTable({
          
          
          #set run name based on text input
          run_name<-input$text
         
          #do the concatenation based on files uploaded and return
          files<-input$file1
          myfiles<-lapply(files$datapath, read.csv, header=FALSE)
          df <- ldply(myfiles, data.frame)
          df2<-df[!(df$V3=="No Tube"),]
          print(observed$input)
          
          #save name
          save_name<-paste(observed$input, "/", run_name, ".csv", sep = "")
          print("SN")
          print(save_name)
          
          write.table(df2, save_name, sep=",", col.names=FALSE,  row.names=FALSE)
          colnames(df2)<-c("Rack", "Position", "Barcode")
          df2
          
      })
    })
  }
  
  shinyApp(ui, server)


```



